Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2017-11-02 TACAS2018/paper.tex
nudge

Since we are interested in synthesising controllers with observer
designs, in this section we will look at checking stability, safety
and the response time in the presence of an observer.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Stability of an observed system}\label{sec:cof_stability}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
In this work we are interested in asymptotic stability: asymptotic
stability is a property that amounts to convergence of the model
executions to an equilibrium point, starting from any states in a
neighborhood of the point. In the rest of the paper we refer to the
stability specification as $\phi_\mathit{stability}$.

%% There are a number of algorithms that can be
%% used for stability analysis~\cite{daes20161,Bessa16}.

A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
is asymptotically stable if all the roots of its characteristic
polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
K$) are inside the unity circle of the complex plane, i.e., their
absolute values are strictly less than one~\cite{astrom1997computer}
(this simple sufficient condition can be generalised, however this is
not necessary in our work).  We express the stability
specification in terms of a check known as
\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
formula over the coefficients of the characteristic polynomial.
%% to select the entries of matrix $K$ so that the closed-loop
%% dynamics are shaped as desired.

In order to be able to apply Jury's criterion,
in the rest of this section, we compute the  
characteristic polynomial of the observer model.
Note that in this section, we consider that the model is
discretized in the time domain, but not in the value domain.
This essentially means that
${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.

%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally

%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
For simplicity of the description, we agregate the noises as follows:
$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
Then, a controllable and observable system will have the following dynamics:
\begin{align}
\scriptstyle
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
\label{eq:observer_LTI}
\end{align}
where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
%, and $k_r$ is a reference gain required by the model.

We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e. with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
\begin{align*}
\mat{A}_{c}=\left[
\begin{array}{cc}
k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
\mat{I}&\mat{0}
\end{array}\right]&&
\mat{A}_{o}=\left[
\begin{array}{ccc}
l_{p-1}-a_{p-1}&&\mat{I}\\
&&\vdots\\
l_0-a_0&&\mat{0}
\end{array}\right]
\end{align*}
where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
This is achieved by the following transformation. Let
\begin{equation}
\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
\end{equation}
We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}' \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\nonumber\\
\vec{y}_k
=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_cf}
\end{align}
{%\setlength{\belowdisplayskip}{0pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}

The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
~are called reachability matrices (of the system and its reachable canonical form, respectively),
and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.

Careful examination of the above matrices reveals that because the $\mat{A}'$ is
upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
separately.  In other words, the characteristic polynomial of the closed loop is
equal to the multiplication of the characteristic polynomials of the controller
and the observer when seen independently.
%
\begin{align*}
P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
\end{align*}

We get the stability specification by using Jury's Criterion on these polynomials.

@@

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
\rangle}$, ${\mat{B}_d}_{\langle C \rangle}$ and ${\mat{C}_d}_{\langle C
\rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
%
%and $\mat{A}_e=\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}$, $\mat{B}_e=\mat{B}_d-{\mat{B}_d}_{\langle C \rangle}$,
%and $\mat{C}_e=\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}$ their corresponding errors.  
Equation \eqref{eq:observer_LTI_cf} becomes:
%
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\mat{B}_{c} \vec{r}_k
+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
where
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c&
\mat{L}_{\langle C \rangle}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
\end{align*}
}
{\setlength{\abovedisplayskip}{0pt}
\begin{align*}
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
\mat{B}_{c}=&\left[\begin{array}{c}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{k}_r\\\mat{0}\end{array}\right]&
\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
\end{align*}
}
The first effect of this new equation is that $\mat{A}'$ is no longer upper
diagonal.  We must therefore compensate for the errors introduced in order
to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_2)$
(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, n],
|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
the perturbed observer.  We note that in the case of stability we only care
about the error with respect to the unit circle, which is equivalent to
upper bounding the estimation of the largest eigenvalue.  Hence, given a
desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
polynomial.
%
\begin{equation}
P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
%
In the case of the reachable eigenvalues, the procedure is the same except
that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_2)$
(\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
apply Jury's Criterion over
%
\begin{equation}
P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}

%% As a final annotation, we remark that the safety specification must be
%% applied to the model described in this section, accounting for the
%% representation errors of the FWL domain.

@@

Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1\ n]$, the settling time of the system is upperbounded by

@@

t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1\ n]

@@

\todo{this description does not mention two synthesis phases, which we should
focus on more.}

>>>>

Since we are interested in synthesising controllers with observer
designs, in this section we will look at checking stability, safety
and the response time in the presence of an observer. A full description of
the theory related to the observer design is provided in appendix \ref{sec:control_theory}
%\subsection{Stability of an observed system}\label{sec:cof_stability}
%In this work we are interested in asymptotic stability: asymptotic
%stability is a property that amounts to convergence of the model
%executions to an equilibrium point, starting from any states in a
%neighborhood of the point. In the rest of the paper we refer to the
%stability specification as $\phi_\mathit{stability}$.
%A discrete-time LTI system (as shown in Sec.~\ref{sec:ssrepresentation})
%is asymptotically stable if all the roots of its characteristic
%polynomial (i.e., the eigenvalues of the closed-loop matrix $A_d - B_d
%K$) are inside the unity circle of the complex plane, i.e., their
%absolute values are strictly less than one~\cite{astrom1997computer}
%(this simple sufficient condition can be generalised, however this is
%not necessary in our work).  We express the stability
%specification in terms of a check known as
%\emph{Jury's criterion}~\cite{fadali}: this is an easy algebraic
%formula over the coefficients of the characteristic polynomial.
%In order to be able to apply Jury's criterion,
%in the rest of this section, we compute the  
%characteristic polynomial of the observer model.
%Note that in this section, we consider that the model is
%discretized in the time domain, but not in the value domain.
%This essentially means that
%${\mat{A}_d}_{\langle C \rangle}=\mat{A}_d$, ${\mat{B}_d}_{\langle C \rangle}=\mat{B}_d$, ${\mat{C}_d}_{\langle C \rangle}=\mat{C}_d, \mat{L}=\mat{L}_{\langle C \rangle}$ and $\mat{K}=\mat{K}_{\langle C \rangle}$.
%%Let us look at observer for a SISO systems as shown in figure \ref{fig:observersystem} where ideally
%%% We will initially assume this for the description of the system and then introduce the errors caused  by misrepresentations.
%For simplicity of the description, we agregate the noises as follows:
%$\eta_1=\nu_1+\nu_1'+\nu_t$ and $\eta_2=\nu_2+\nu_2'$,
%where $\nu_1$ and $\nu_2$ are the quantization noises introduced by the ADC and the DAC, $\nu_t$ is the noise introduced by the delay, and $\nu_1'$ and $\nu_2'$ are quantization noises caused by roundoffs in the FWL operations.
%Then, a controllable and observable system will have the following dynamics:
%\scriptstyle
%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_{k+1}
%=\left [\begin{array}{cc}\mat{A}_d-\mat{B}_d\mat{K}&\mat{B}_d\mat{K}\\ \mat{0}&\mat{A}_d-\mat{L}\mat{C}_d\end{array}\right]
%\left [\begin{array}{c}\vec{x}\\ \vec{x}_e \end{array}\right]_k
%+\left [\begin{array}{c}\mat{B}_dk_r\\ \mat{0} \end{array}\right] \vec{r}_k
%+\left [\begin{array}{cc}\mat{B}_dk_r&\mat{0}\\ \mat{0}&-\mat{L}\end{array}\right]\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]
%\label{eq:observer_LTI}
%where $\vec{x}_e=\vec{x}-\hat{\vec{x}}$ is the estimation error of the state space by the observer.
%%, and $k_r$ is a reference gain required by the model.
%We want the state space dynamics in reachable form ($\mat{A}_c$) and the observer error dynamics in observable form ($\mat{A}_o$), i.e. with dynamics whose coefficients are represented solely by those of the characteristic polynomial as follows:
%\mat{A}_{c}=\left[
%k_{p-1}-a_{p-1}&\begin{array}{cc}\cdots&k_0-a_0\end{array}\\
%\mat{I}&\mat{0}
%\end{array}\right]&&
%\mat{A}_{o}=\left[
%\begin{array}{ccc}
%l_{p-1}-a_{p-1}&&\mat{I}\\
%&&\vdots\\
%l_0-a_0&&\mat{0}
%\end{array}\right]
%where $\sum_{i=0}^p a_iz^i$ is the characteristic polynomial of the plant and $a_p=1$.
%This is achieved by the following transformation. Let
%\left[\begin{array}{c}\vec{x}'\\ \vec{x}_e'\end{array}\right]=
%\left[\begin{array}{cc}\mat{T}_c & \mat{0}\\\mat{0} & \mat{T}_o\end{array}\right] 
%\left[\begin{array}{c}\vec{x}\\ \vec{x}_e\end{array}\right]
%We can transform equation \eqref{eq:observer_LTI} into the equivalent canonical form
%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
%=& \left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]
%\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
%+\mat{B}' \vec{r}_k
%+\mat{B}_{\eta}\left [\begin{array}{c}\vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
%\nonumber\\
%\vec{y}_k
%=& \mat{C}_{t}\vec{x}_k% + \mat{D}_{d}\vec{u}_k
%\label{eq:observer_LTI_cf}
%{%\setlength{\belowdisplayskip}{0pt}
%\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
%\mat{A}_{o}=&\mat{T}_o\left(\mat{A}_d-\mat{L}\mat{C}_d\right)\mat{T}_o^{-1}\\
%\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}&\mat{B}_{o}\\ \mat{0}&\mat{A}_{o}\end{array}\right]&
%\mat{B}_{o}=&\mat{T}_c\mat{B}_d\mat{K}\mat{T}_o^{-1}\\
%\mat{B}'=&\left[\begin{array}{c}\mat{T}_c\mat{B}_d\mat{k}_r\\\mat{0}\end{array}\right]&
%\mat{B}_{\eta}=&\left[\begin{array}{cc}\mat{T}_c\mat{B}_d\mat{k}_r&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}\end{array}\right]\\
%\mat{T}_c=&\mat{R}_{cf}\mat{R}^{-1}&
%\mat{T}_o=&\mat{W}_o^{-1}\mat{W}_{of}\\
%\mat{C}_t=&\mat{C}_d\mat{T}_c&
%\mat{L}=& \mat{T}_o^{-1}\left[ \begin{array}{ccc}l_1&\cdots&l_n\end{array}\right]^T
%The matrices $\mat{R}$%$\mat{R}=\left[\begin{array}{cccc} \mat{B} & \mat{A}\mat{B} & \cdots & \mat{A}^{p-1}\mat{B} \end{array}\right]$
%~and $\mat{R}_{cf}$%$\mat{R}_{cf}=\left[\begin{array}{cccc} mat{B}_c & \mat{A}_c\mat{B}_c & \cdots & \mat{A}_c^{p-1}\mat{B}_c \end{array}\right]$
%~are called reachability matrices (of the system and its reachable canonical form, respectively),
%and $\mat{W}_o$%$\mat{W}_o=\left[\begin{array}{c} mat{C}\\ \mat{C}\mat{A}\\ \vdots \\ \mat{C}\mat{A}^{p-1} \end{array}\right]$
%~and $\mat{W}_{of}$%$\mat{W}_{of}=\left[\begin{array}{c} mat{C}_o\\ \mat{C}_o\mat{A}_o\\ \vdots \\ \mat{C}_o\mat{A}_o^{p-1} \end{array}\right]$
%~are its observability matrices  (of the system and its Observable Canonical Form respectively)~\cite{astrom1997computer}.
%Careful examination of the above matrices reveals that because the $\mat{A}'$ is
%upper block diagonal, the spectrum of $\mat{A}'$ is equal to the union of
%the spectrum of $\mat{A}_{c}$ and $\mat{A}_{o}$, which can be calculated
%separately.  In other words, the characteristic polynomial of the closed loop is
%equal to the multiplication of the characteristic polynomials of the controller
%and the observer when seen independently.
%P(z)=P_K(z)P_L(z)=\left(z^p+\sum_{i=0}^{p-1}{(a_i-k_i)z^{i}}\right) \left(z^p+\sum_{i=0}^{p-1}{(l_i-a_i)z^{i}}\right)
%We get the stability specification by using Jury's Criterion on these polynomials.

@@

When our observer is implemented using a finite precision controller, new
problems arise due to the FWL effects.  Let ${\mat{A}_d}_{\langle C
\rangle}$, ${\mat{B}_d}_{\langle C \rangle}$ and ${\mat{C}_d}_{\langle C
\rangle}$ be the dynamics represented in $\mathbb{R}_{\langle C\rangle}^*$,
Equation \eqref{eq:observer_LTI_cf} becomes:
%
\begin{align}
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_{k+1}
=& \left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]
\left [\begin{array}{c}\vec{x}'\\ \vec{x}_e' \end{array}\right]_k
+\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]\left [\begin{array}{c} \vec{r}_k + \vec{\eta}_2\\ \vec{\eta}_1\end{array}\right]\nonumber\\
\vec{y}_k=&\mat{C}_{t}\vec{x}_k'% + \mat{D}_{d}\vec{u}_k
\label{eq:observer_LTI_FWL_cf}
\end{align}
where $\mat{T}_c$ and $\mat{T}_o$ trasfrom the system into canonical form~\cite{Astrom08} and
{\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt}
\begin{align*}
\mat{A}_{c}=&\mat{T}_c\left(\mat{A}_d-\mat{B}_d\mat{K}\right)\mat{T}_c^{-1}&
\mat{A}_{o}=&\mat{T}_o\left({\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}{\mat{C}_d}_{\langle C \rangle}\right)\mat{T}_o^{-1}\\
\mat{B}_{o}=&\mat{T}_c{\mat{B}_d}_{\langle C \rangle}\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}&
\mat{B}_{e}=&\mat{T}_c(\mat{B}_d-{\mat{B}_d}_{\langle C \rangle})\mat{K}_{\langle C \rangle}\mat{T}_o^{-1}\\
\mat{A}_{e}=&\mat{T}_o\left(\mat{A}_d-{\mat{A}_d}_{\langle C \rangle}-\mat{L}_{\langle C \rangle}\mat{C}_e\right)\mat{T}_o^{-1}&
\mat{C}_{e}=&\mat{C}_d-{\mat{C}_d}_{\langle C \rangle}\\
\mat{C}_t=&\mat{C}_d\mat{T}_c
\end{align*}
}
{\setlength{\abovedisplayskip}{0pt}
\begin{align*}
\mat{A}'=&\left [\begin{array}{cc}\mat{A}_{c}+\mat{B}_{e}&\mat{B}_{o}\\ \mat{A}_{e}&\mat{A}_{o}\end{array}\right]&
\mat{B}'=&\left[\begin{array}{cc}\mat{T}_c{\mat{B}_d}_{\langle C \rangle}&\mat{0}\\\mat{0}&-\mat{T}_o\mat{L}_{\langle C \rangle}\end{array}\right]
\end{align*}
}
The first effect of this digitalization is that $\mat{A}'$ is no longer upper
diagonal.  We must therefore compensate for the errors introduced in order
to find a stable solution.  We can use Gershgoring disks~\cite{van1996matrix} to limit the error
in the expected eigenvalues.  Let $\delta_o=\max(\norm{{\mat{A}_e}_{i,*}}_1)$
(\emph{i.e.} the largest row norm in $\mat{A}_e$) be the largest error bound
for any eigenvalue in $\mat{A}_e$.  Then $\forall i \in [1, n],
|{\lambda_o}_{i}-\hat{\lambda_o}_{i}|<\delta_o$,where ${\lambda_o}_{i}$ are the
true eigenvalues of the observer and $\hat{\lambda_o}_{i}$ the eigenvalues of
the perturbed observer.  We note that in the case of stability we only care
about the error with respect to the unit circle, which is equivalent to
upper bounding the estimation of the largest eigenvalue.  Hence, given a
desired upper value $\overline{\lambda}$, we apply Jury's criterion on the
polynomial.
%
\begin{equation}
P_o'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_o)\overline{\lambda}
\end{equation}
%
In the case of the reachable eigenvalues, the procedure is the same except
that we obtain our bound $\delta_c=\max(\norm{{\mat{A}_e}_{*,i}+{\mat{B}_e}_{*,i}}_1)$
(\emph{i.e.} the largest column norm in $ \left[\begin{array}{c}\mat{A}_e\\ \mat{B}_e\end{array}\right]$) and
apply Jury's Criterion over
%
\begin{equation}
P_r'=\sum_{j=0}^p c_j\overline{\lambda'}^{p-j}s^j : \overline{\lambda'}=(1+\delta_c)\overline{\lambda}
\end{equation}

@@

Given a set of eigenvalues for a discrete time model of an $n^{th}$ order system $\lambda_i =e^{\omega_i}: i \in [1, n]$, the settling time of the system is upperbounded by

@@

t_s<-log_{\overline{\lambda}}({p_s}) : \overline{\lambda} = \max(|\lambda_i|) \wedge \overline{\lambda}<1,\ \forall i \in [1, n]

@@

\todo{I assume the optimization problem is something like: ``find a controller and an observer that minimize some cost function''. What is the cost function in this case? I guess you want something like the
  difference between the current candidate and the general solution? How would we capture that?}

\todo{What is the optimization alg that you use? Point 4 below doesn't specify much.}
